---
title: "성인남자 LMS 분석 -VO2max"
author: "Yonghee Lee"
date: "2018년 9월 26일"
output:
    knitr:::html_vignette:
    number_sections: yes
    toc: yes
vignette: >
  %\VignetteIndexEntry{An Introduction to The printr Package}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#options(Encoding="UTF-8")
library("readxl")
library("knitr")
library(gamlss)
library(dplyr)
library(qwraps2)
options(qwraps2_markup = "markdown")
#setwd("D:/ylee19067/Dropbox/working/teaching/2018F/통계상담I/sportsdata/adult")
varinfo <- read_excel("2018 통계컨설팅 이용희교수님_청소년,성인,노인 변수설명_180910.xlsx",3,col_names = TRUE,
                         col_types = "text", na = "")
our_summary1 <-
  list("age" =
         list("min" = ~ min(age,na.rm = TRUE),
              "max" = ~ max(age,na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(age,na_rm = TRUE)),
       "Height" =
         list("min" = ~ min(Height,na.rm = TRUE),
              "max" = ~ max(Height,na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(Height,na_rm = TRUE)),
       "weight" =
         list("min" = ~ min(weight,na.rm = TRUE),
              "max" = ~ max(weight,na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(weight,na_rm = TRUE)),
       "BMI" =
         list("min" = ~ min(BMI,na.rm = TRUE),
              "max" = ~ max(BMI,na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(BMI,na_rm = TRUE)),
        "VO2max" =
         list("min" = ~ min(VO2max,na.rm = TRUE),
              "max" = ~ max(VO2max,na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(VO2max,na_rm = TRUE))
         )
```

# 자료 읽기 
```{r}
adult0 <- read.csv("adult.csv", header=T, sep=",")
adult <- filter(adult0, sex==1)
```



# 인구적 변수 

```{r results = 'asis' , echo=FALSE}
whole <- summary_table(adult, our_summary1)
whole
```



#  `VO2max` 분석

## 기초통계 분석 및 이상치제거
```{r}
adult1 <- select(adult,age,VO2max)
summary(adult1)
dim(adult1)
adult1<- na.omit(adult1)
adult1 <- filter(adult1, VO2max < 9998)
adult10 <- adult1
summary(adult10)
dim(adult10)
mm <- mean(adult1$VO2max)
sdd <- sd(adult1$VO2max)
adult1 <- filter(adult1, VO2max > mm-3*sdd & VO2max <mm+3*sdd )
summary(adult1)
dim(adult1)
plot(VO2max~age, data=adult1, pch = 15, cex = 0.5, col = gray(0.5))
```


## LMS centile curve

### fitting for data within 3SD
```{r}
m1 <- lms(VO2max,age, data=adult1, trans.x=T, k=2)
summary(m1)
```

### fitting for all data
```{r}
m10 <- lms(VO2max,age, data=adult10, trans.x=T, k=2)
summary(m10)
```


#### diagnostics
```{r}
round(Q.stats(m1, xvar=adult1$age),3)
wp(m1, xvar=adult1$age, n.inter=9)
```
### different fits


Fit with just Normal 
```{r}
m2 <- lms(VO2max,age, data=adult1, trans.x=T, k=2, formula = VO2max ~ ps(age), sigma.formula = ~ps(age), nu.formula = ~ps(age), tau.formula = ~ps(age), family = "NO")
summary(m2)
centiles.com(m1, m2, xvar=adult1$age, legend = TRUE , color=T)
```

Fit with cubic spline
```{r}
m3 <- gamlss(formula = VO2max ~ cs(age), data=adult1, trans.x=T, k=2, sigma.formula = ~cs(age), nu.formula = ~cs(age), tau.formula = ~cs(age), family ="BCPEo")
summary(m3)
centiles.com(m1, m3, xvar=adult1$age, legend = TRUE , color=T)
```

### prediction curve

```{r}
fittedPlot(m1 ,x=adult1$age)
```

### centile curve

```{r}
centiles(m1,adult1$age,cent=c(2,5,10,25,50,75,85,90,95,98) )
```

### centile prediction

- case 1: For given new x-values and given percentage centiles, calculates a matrix containing the centile values for y.
- case 2: For given new x-values and standard normalized centile values, calculates a matrix containing the centile values for y.
- case 3: For given new x-values and new y-values calculates the z-scores [one Z-score for each (x; y) pairs].

`case 1`

```{r}
newage<-c(24,34,44,54,61.5) 
mat <- centiles.pred(m1, xname="age", xvalues=newage, cent=seq(5,95,5))
mat
```

```{r}
mat0 <- centiles.pred(m10, xname="age", xvalues=newage, cent=seq(5,95,5))
mat0
```
`case 2`

```{r}
centiles.pred(m1, xname="age", xvalues=newage, type="standard-centiles",
dev = c(-4, -3, -2, -1, 0, 1, 2, 3, 4),plot = TRUE, legend=FALSE )
```


`case 3` z-score

```{r}
zscore <- z.scores(m1, x=adult1$age, y=adult1$VO2max)
head(zscore,50)
```

# 구간별  추정

```{r}
centiles.split(m1,xvar=adult1$age,xcut.points=c(30,40,50,60),cent=seq(5,95,5))
```


# 변수설명

```{r}
library(printr)
knitr::kable(varinfo , caption = '변수설명')
```
